---
title: "Meta-Analysis of Infection Fatality Ratio"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Meta-Analysis of Infection Fatality Ratio}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(outbreaktools)
library(brms)
```

A re-interpreation of [this excellent post](https://medium.com/@gidmk/what-is-the-infection-fatality-rate-of-covid-19-7f58f7c90410) with methods based [on this book on meta-analysis](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/bayesian-meta-analysis-in-r-using-the-brms-package.html).

## Data

The following are the data from a systematic review of Infection Fatality Ratios (IFR). 
As a reminder, IFRs are lower than Case Fatality Ratios (CFRs) because they include asymptomatic people. 
With roughly 30% of the population being asymptomatic (this needs another meta-analysis), there must be some adjustments made.

```{r}
library(dplyr)
dat_meta <- tibble::tribble(
  ~"Author", ~"TE", ~"ci95",
  "Jung et al", .7, 0.52,
  "CEBM", .2, .1,
  "Ferguson et al", 1, .62,
  "Nishiura et al", .45, .09,
  "Tian et al", 1.15, 1.15,
  "Verity et al", .66, .6,
  "Russell et al", .6, .4,
  "Bendavid et al", .2, .04,
  "New York City", .93, .02,
  "Rinaldi et al", 1.29, .72,
  "Roques et al", .8, .45,
  "Villa et al", 1.6, .5,
  "Modi et al", .95, .75
) %>% 
  mutate(seTE = ci95/1.96)
```

# Priors

Set some relatively tight priors.

```{r}
priors <- c(prior(normal(.01,.002), class = Intercept),
            prior(cauchy(0,0.1), class = sd))
```

# Model Fitting

Fit it.

```{r}
m <- brm(TE|se(seTE) ~ 1 + (1|Author),
             data = dat_meta,
             prior = priors,chains = 4,cores = 4,
             iter = 4000, refresh = 0)
```

```{r}
pp_check(m, nsamples = 25)+
  ggplot2::theme_minimal()
```

```{r}
summary(m)
```

```{r}
post_samples <- posterior_samples(m, c("^b", "^sd"))
names(post_samples) <- c("smd", "tau")
```

```{r}
quantz <- quantile(post_samples$smd, c(.05, .5, .95))*100
hist(post_samples$smd*100, col = "grey", main = "Posterior Distribution of Infection Fatality Rate", adj = 0, ylab = "Frequency", xlab = "IFR")
abline(v =quantz, lty = 2, col = "orange")
text(x = quantz, y= 10,labels = round(quantz,2))
```


```{r}
quantile(post_samples$smd, c(.05, .5, .95))*100
```

